% E. Dunham -- Resume
% Contents Copyright (C) 2014 - 2016, E. Dunham

% LaTeX code for rendering the resume is distributed under the MIT license.
% See LICENSE.txt. It means you can use the code for whatever you want,
% including your own resume, but I'm not liable if it catches your computer on
% fire.

% Template originally developed by E. Dunham
% https://github.com/edunham/resume/blob/master/resume.tex

\documentclass[11pt]{article} % Set default font size to 11pt
\usepackage[utf8]{inputenc}
\input{preamble}
\begin{document}

\centerline{{\Huge \bf Ariel Ben-Yehuda}}
\bigskip

\contact{ariel.byd@gmail.com}
        {progmathnotes.wordpress.com}
        {github.com/arielb1}
        {Tel-Aviv, Israel}

\heading{About}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

My résumé isn't yet long enough to stand out on its own, so let me introduce myself. \\

I'm Ariel. I have been programming for quite some time and I have grown to understand and love math quite well since I started my degree at age 14. I'm quite good at finding information, learning \& understanding new things, and figuring out solutions. I consider myself quite good at working in teams, as long as I have space to do things on my own. \\

I enjoy computer things, math, geeking out, reading about science in the Internet (never got around to Actually Doing It, but that's your chance), Kalafina's songs, and watching Nature. \\

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As I said, I know quite a lot of things and I am always ready to learn new stuff, but here are some things I am very good at: \\

\skill{Programming}
      {Rust, Python, C/\CPP}

\skill{System Administration}
      {Everything Linux Userspace, Debian, Red Hat, bash, ssh, etc.}

\skill{Collaboration}
      {Git, IRC, decent Technical Writing}

\skill{Mathematics}
      {Linear Algebra, Formal Logic, Cryptography}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Check Point}
           {Software Developer - Platforms Team}
           {08/2014 - 12/2016}

Handled the integration of Check Point's solution with Linux, including rewriting the build infrastructure, backporting security and functionality patches, and hunting down and solving many, many hard-to-find integration bugs.

\experience{Mozilla Research}
           {Rust Compiler Team Member}
           {11/2015 - Present}

Developing the Rust programming language \& compiler - a new, safe, fast \& productive \CPP-class language.

Designed and helped design parts of the type-system and middle-end. Improved compiler performance by tens of percents. Reduced compiler stack usage by over 16x. Took responsibility and fixed many compiler bugs and regressions.

\end{description}


\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Tel-Aviv University}
           {}
           {2011-2016}

           BSc in Mathematics and Computer Science including Logic, Machine Learning, Parallel Computation.

\end{description}

\heading{Security Bugs}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Tarsnap Path NUL overflow}
           {}
           {04/2014}

No CVE, refs: \\
   - http://www.daemonology.net/blog/2015-08-21-tarsnap-1000-exploit-bounty.html \\
   - https://github.com/Tarsnap/tarsnap/commit/c3a7532770e6ab5d9310d4104962113566099305 \\
\end{description}

%\experience{Linux.Conf.Au}
%           {}
%           {02/2016}
%
%    ``Life is better with Rust's community automation''

%\experience{SeaGL}
%           {}
%           {10/2015}
%
%    ``You Should Speak'', technical presentation tutorial

%\experience{O'Reilly OSCON}
%           {}
%           {07/2015}
%
%    ``First Impressions: The Value of the ``Noob'''', Ignite talk

%\experience{OpenWest}
%           {}
%           {05/2015}
%
%    ``Human Hacking'', ``Thinking in Git'', and ``Teaching DevOps to
%    University Students''

%\experience{LinuxFest Northwest}
%           {}
%           {04/2015}
%
%    ``Algorithmic Complexity and You'', ``Thinking in Git''

%\experience{Southern California Linux Expo (SCALE)}
%           {}
%           {02/2015}
%
%    ``Human Hacking''

%\experience{Seattle GNU/Linux Conference}
%           {}
%           {10/2014}
%
%    ``Human Hacking'', ``Intermediate IRC'', and ``Thinking in Git''

%\experience{O'Reilly OSCON}
%           {}
%           {07/2014}
%
%    ``DevOps for University Students''

%\experience{Portland State University Association for Computing Machinery}
%           {}
%           {05/2014}
%
%    ``Git Workshop''

%\experience{LinuxFest Northwest}
%           {}
%           {04/2014}
%
%    ``Teaching DevOps to University Students''

% \end{description}
\end{document}
